Missing data: Current practice in football research and recommendations for improvement

### 2020-09-05 paper/paper.Rmd
edit results section.
edit first paragraph of the discussion.

Of the 199 articles screened, 136 were deemed eligible, representing
\~10% of the articles found (Figure X). XX articles (of the 199) were
excluded due to not meeting the inclusion criteria. The proportion of
articles that reported missing data was 5.9% (95% confidence interval;
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration--especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).

@@

Our survey of 136 articles published on football related topics found
that only about one in 20 papers reported missing data. It is reasonable
to assume that this result is representative of current practices in the
wider sports science literature. This finding may be largely explained
by a lack of awareness and education on missing data practices (https://bjsm.bmj.com/content/early/2020/08/19/bjsports-2020-102607.abstract), 
similar to other areas of sciences (refs-education and
ecology examples)(2). Below we discuss several practices to avoid in
relation to missing data, and provide recommendations for exploring,
visualising and reporting missingness.

>>>>

Of the 199 articles screened, 136 met the inclcusion criteria, representing
\~10% of the articles found (see Supplement 2, Figure 1). The proportion of
articles that reported missing data was 5.9% (95% confidence interval;
X% to X%) or 8/136. Of the articles that did not mention missing data
(128/136), 7.1% (3.3% to 13.1%) or 9/128 shared their dataset, making
it difficult to determine whether there was any missingness. While the
absence of a missing data statement does not necessarily mean missing
data are not being reported, it does suggest that this aspect of the
analysis process receives little consideration--especially in contrast
to many of the papers that included (potentially meaningless) tests of
normality (e.g., Kruskall-Wallis test).

@@

Our survey of 136 articles published on football related topics found
that only about one in 20 papers reported missing data. It is reasonable
to assume that this result is representative of current practice in the wider sports science literature. 
The low proportion of papers reporting missingness could be explained by a lack of awareness and education on missing data (https://bjsm.bmj.com/content/early/2020/08/19/bjsports-2020-102607.abstract), 
similar to other areas of sciences (refs-education and
ecology examples)(2)**references needed**. Below we discuss several practices to avoid in
relation to missingness, and provide recommendations for exploring,
visualising and reporting missing data.
